Variational Monte Carlo on bosonic systems

### 2018-01-27 project_1/article/article.tex
Add explicit expressions for derivates
	This is for the interaction functions.

                r_{km} = |r_k - r_m|

@@

                = \frac{r_k - r_m}{|r_k - r_m|}.

@@

            Working in spherical coordinates we see that $u(r_{km})$ will only
            be a function of radii of particles $k$ and $m$. The gradient thus
            simplifies to the radial contribution giving

@@

@@

                \frac{r_k - r_m}{r_{km}}\tpl{{r_{km}}}^2 u(r_{km})

>>>>

                r_{km} = |\vf{r}_k - \vf{r}_m|

@@

                = \frac{r_k - r_m}{|\vf{r}_k - \vf{r}_m|},

@@

            where in spherical coordinates $\vf{r}_k = r_k\vf{e}_r$.  The
            gradient of $u(r_{km})$ thus simplifies to only include the radial
            contribution.

@@

                    \frac{r_k - r_m}{r_{km}}
                    \partial_{{r_{km}}}^2 u(r_{km}) \\
                    + \frac{r_{km}^2}{r_{km}^3} \tpl{{r_{km}}} u(r_{km})
                    \frac{(r_k - r_m)^2}{r_{km}^2}
                    \partial_{{r_{km}}}^2 u(r_{km}) \\
                    \frac{2}{r_{km}}\tpl{{r_{km}}}u(r_{km})
                    + \partial_{{r_{km}}}^2u(r_{km}).
            We now take the derivate with respect to $r_{km}$ of the interaction
            functions $u(r_{km})$ to find the closed form expressions. We get
                \partial_{r_{km}}u(r_{km})
                \partial_{r_{km}}
                \ln\Biggl(
                    1 - \frac{a}{r_{km}}
                \partial_{r_{km}}
                \ln\Biggl(
                    \frac{1}{r_{km}}
                    (r_{km} - a)
                \partial_{r_{km}}
                    \ln(r_{km} - a)
                    - \ln(r_{km})
                \frac{1}{r_{km} - a} - \frac{1}{r_{km}} \\
                \frac{a}{r_{km}(r_{km} - a)} \\
                \partial_{r_{km}}^2u(r_{km})
                &= a\Bigl(
                    \partial_{r_{km}}\frac{1}{r_{km}}
                \Bigr)
                \partial_{r_{km}}\frac{1}{r_{km} - a}

@@

                + a\frac{1}{r_{km}}
                \Bigl(
                    \partial_{r_{km}}\frac{1}{r_{km} - a}
                \Bigr) \\
                -\frac{a}{r_{km}^2(r_{km} - a)}
                -\frac{a}{r_{km}(r_{km} - a)^2} \\
                - \frac{2a(r_{km} - 1)}{r_{km}^2(r_{km} - a)^2}.
